---
title: "Balance and Attrition Results"
output:
  pdf_document:
    keep_tex: yes
knit: (function(input, ...) rmarkdown::render(input, knit_root_dir = here::here(), ...))
header-includes:
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{placeins}
    - \usepackage{colortbl}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage[utf8]{inputenc}
    - \usepackage{makecell}
    - \usepackage{xcolor}
params:
    cache: FALSE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = FALSE,
  cache   = params$cache,
  warning = FALSE,
  message = FALSE
)

# Helper: wrap a stripped-table .tex file back into a float with a caption
include_tex_table = function(path, caption = NULL) {
  lines = readLines(path)
  out = c(
    "\\begin{table}[htbp]",
    if (!is.null(caption)) sprintf("\\caption{%s}", caption),
    lines,
    "\\end{table}"
  )
  cat(out, sep = "\n")
}
```

## Main Balance Table


This is unchanged - I still need to edit the layout and move sections, I've just included it for completeness.
```{r main-balance-table, results="asis"}
include_tex_table("presentations/tables/comp-balance-table.tex", "Balance Table")
```

\FloatBarrier

## Endline Belief Sample Balance

This is the balance on the census/monitored variables for the HHs in the belief sample. It's  
possible we might be able to add a couple more variables here. 

```{r belief-balance-table, results="asis"}
include_tex_table(
  "presentations/tables/belief-sample-balance-table.tex",
  "Belief Sample Balance"
)
```

\FloatBarrier

## Baseline Sample Balance

We can match the _sampling frame_ of 4,185 into the monitored sample, but we
cannot match the 1,995 individuals that _completed the baseline survey_ into the
monitored sample. Therefore, we cannot directly recreate balance using the same
outcomes for the 1,995. We could use a mix of other variables to get as close as
possible. I haven't done this yet.



## Knowledge Table Attrition

This tests for differential attrition into the knowledge table sample for the 255 
that do not have a knowledge table entry. The sample matches our analysis sample - i.e. 
all 2,659 that are in the endline sample with SMS control.

```{r knowledge-attrition, results="asis"}
include_tex_table(
  "presentations/rf-tables/main-specs/know_table_attrition_spec_tbl.tex",
  "Knowledge Table Attrition by Treatment"
)
```


## Knowledge Table Attrition - Different Sample

The 1,141 (although actually slightly larger as we don't subset to knowing people > 0, so 1204) + 252

```{r knowledge-attrition-diff-sample, results="asis"}
include_tex_table(
  "presentations/rf-tables/main-specs/know_table_A_attrition_spec_tbl.tex",
  "Knowledge Table Attrition by Treatment"
)
```




\FloatBarrier
## Monitoring Attrition (Dropped from SurveyCTO)

This table tests for differential attrition into the monitored sample for the
989 that do not have a monitoring entry. The sample matches our analysis sample
- i.e. 9,805 + 989 = 10,794. 

```{r monitoring-attrition, results="asis"}
include_tex_table(
  "presentations/rf-tables/main-specs/rf_attrition_cto_tbl.tex",
  "Monitoring Attrition by Treatment"
)
```

\FloatBarrier